What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Example of function definition in eval

>>>>

\mypara{Function definition.} This corresponds to minimized expression \c{FUN}. Package \emph{Rcpp} is used to easily interface C++ and R and it uses \eval to bind C++ functions and classes to R objects.
For instance, \c{.makeCppMethods} create a R function for each C++ method named \c{what} of a given class.
\begin{lstlisting}
methods[[what]] <- eval(substitute(
	function(...) .CppObject$WHAT(...), list(WHAT = as.name(what))),
	env)
\end{lstlisting}
